### 2023-11-15 related.tex
Updates from Overleaf
Fix typos

In the realm of error messages for constraint-based inference, work on the Helium Haskell compiler \cite{heeren2003} offers two constraint solvers based on the desired feedback: a global, type graph-based constraint solver which provides detailed error messages, and a lightweight and high-performance greedy solver. When using the global constraint solver, various heuristics can tune the likelihood of different parts of programs reported as error sources.
Recently, \citet{bhanuka2023} model the flow of type information throughout the program using subtyping constraints to produce detailed error messages when unification fails.
Our focus in this paper has not be on the error messages displayed on-screen, about which we make no specific claims.
It may, however, be beneficial to indicate to the user from where in the program type suggestions originated via type provenances. Documenting the flow of type information would require using assymetric constraints rather than typical bidirectional equality constraints.

>>>>

In the realm of error messages for constraint-based inference, work on the Helium Haskell compiler \cite{heeren2003} offers two constraint solvers based on the desired feedback: a global, type graph-based constraint solver which provides detailed error messages, and a lightweight and high-performance greedy solver. When using the global constraint solver, various heuristics can tune the likelihood of different parts of programs reported as error sources.
Recently, \citet{bhanuka2023} model the flow of type information throughout the program using subtyping constraints to produce detailed error messages when unification fails.
Our focus in this paper has not been on the error messages displayed on-screen, about which we make no specific claims.
It may, however, be beneficial to indicate to the user from where in the program type suggestions originated via type provenances. Documenting the flow of type information would require using asymmetric constraints rather than typical bidirectional equality constraints.
